\section{Reviewer comments}

2. The model is not described with enough detail. A technical report or another publication should be cited that fully describes the model.

4. L176: Unclear what the time step information (2000-01-01 20:20:20) means - please explain.

5. L177ff: What are the "first" and "second" altitudes mentioned?

6. L204: DES should have 1-2 standard references (textbooks)

7. L234: I understand that with a StdDev of 10 percent the influence of the variability in processes is negligible compared to the role the weather plays, but when I look at the processes in Table 4 I am surprised that the times can be realized so accurately. I would expect that one needs much higher StdDev to model most of these processes with realistic statistics. Please comment.

8. L246: What are the key performance indicators for an offshore wind park that you can calculate with your model?

9. L254ff: Is it possible to run the simulation with more than one vessel?

10. L266: "total duration of the simulation runs ... is about 90 minutes" - you mean wall time?

11. Table 4: What statistical distributions are used here (Gaussians?)

12. l294: "which proves that the weather data has been implemented in a correct fashion." - I do not see a proof here, although it certainly "suggests" this.


In addition, a few minor issues as well:

- L39: "HAS been developed"
- Table 1: "Civil work" - What is this?
- L67: Abbreviation "MILP" should be explained before use
- L80: "Firstly" does not exist
- L154: "In this paper THE installation strategy with the pre-assembly at harbour HAS been considered."
- L175: "These measurements are related to the following parameters:" - unclear, please rephrase
- L189: "has been defined for each resource based on"
- L191: "DOES NOT exceed"
- L197: "the probability OF not having"
- L222: "a DES HAS been developed"
- L223f: "A validation case HAS been developed in partnership with an industrial PARTNER that provided..."
- L230: "Stochastic input variables"
- L247: "for various starting DATES"
- Table 4: "HAS been applied"
- L308: "that can improve planning"
- L318: "This is the STARTING point..."
