\subsection{Model description}
In this paper, one jacket foundation, four piles, two tower segments, one nacelle, one rotor hub and three rotor blades per OWT are considered. There are four distinct phases in the logistics chain considered in the simulation model.
\begin{enumerate}
\item Pre-pilling phase -- Height piles are loaded to the transport ship or feeder vessel at port and transported to the offshore site. Then, four piles are transfered to the jack-up vessel. Finally, piles are driven one by one into the sea bed. The transport ship or feeder vessel waits until the first set of piles have been driven into the sea bed. Then the second set of four piles are transfered to the jack-up vessel. At this point, the feeder vessel can sail back to the port while the jack-up vessel keeps installing the transferred piles. Here, it should be noted that the feeder vessel after being loaded can only leave the port if and only if the weather is good enough based on workability and time window requirements for the transport (condition 1) and transfer of the four piles onto the jack up vessel (condition 2). The weather is to be checked for each pile to be driven one by one. Jacket phase will start after 20 piles (piles for five OWTs) have been driven at the offshore site. 

\item Jacket phase -- The activity start by loading two jacket foundations at the port and then transport them to the offshore site. At the offshore site, the foundations are installed and grouted one by one. Grouting is the process of making a structural connection between a jacket and the piles that have been driven or drilled into the seabed. Transport and assembly of topside elements will start after five jacket foundations have been installed and grouted at the offshore site.  

\item Transport and assembly phase -- Here, wind turbine components (blades, tower sections, nacelles and hubs) required for three OWTs are loaded at the port and transported to the staging area close to the offshore site. The storage limit at staging area correspond to components of five OWTs. At the staging area, components will be unloaded, stored and assembled if necessary. The number of lifts at the offshore site depends on the assembly strategy selected. There are mainly three assembly strategies currently used in the offshore wind industry:

\begin{enumerate}
\item Rotor Star (RS) -- Three blades and hub are pre-assembled to form a rotor in the staging area. Then, rotor is transported to offshore site.
\item Single Blade (SB) -- All the wind turbine parts are transported to the offshore site and installed one by one.
\item Bunny Ears (BE) -- Two blades are pre-assembled forming a bunny ears in the staging area. Then, the last blade is installed independently at the offshore site.
\end{enumerate}

\item Installation phase -- Components required for the assembly of one OWT are loaded onto the jack-up vessel and transported to the offshore site. Then, the jack-up vessel install the parts of the OWT one by one at the offshore site and sail back to the staging area until all the OWTs are installed.
\end{enumerate}