\subsection{Two approaches}
Two approaches have been considered in the DES. They are differing by the way to use the metocean historical time series.
In the first approach (deterministic workability), environmental data are directly used in the DES to assess if an activity can be started based on weather window and workability criterion while in the second approach (probabilistic workability) probabilities to work are previously computed.

Approach 1 has the advantage to perform assessments on historical data which allow the calibration of the simulation model based on past projects but does not allow the scheduling of new projects. Contrarely, approach 2 is designed to be used for planning of new projects as it is using working probabilities computed on monthly base. These probabilities to work have been computed for each activity considering the workability and weather window restrictions.






???? Here the average monthly workability has been implemented in the simulation model. 

If there are two activities to be carried out one after another without interruption, it requires the implementation of conditional probability.  
In probability theory, \cite{Thalemann2012}, a conditional probability measures the probability of an event given that another event has occurred. Following Kolmogorov definition, given two events A and B, the conditional probability of A given B is defined as the quotient of the probability of the joint of events A and B, and the probability of B, see equation \ref{eqn:kolmogorov}.

\begin{equation}
\label{eqn:kolmogorov}
P \left(A \vert B \right) = \frac{P \left(A \cap B \right)}{P \left( B \right)}
\end{equation}

The tree diagram shown in Fig. \ref{fig:condprob} may represent a series of independent events or conditional probabilities. Each node on the diagram represents an event and is associated with the probability of that event. The root node represents the certain event and therefore has probability 1. Each set of sibling nodes represents an exclusive and exhaustive partition of the parent event. The probability associated with a node is the chance of that event occurring after the parent event occurs. The probability that the series of events leading to a particular node will occur is equal to the product of that node and its parents' probabilities.

In this paper, the upper branch of the tree is used in order to compute the workability of two successive activities. For example, considering the pre-pilling phase, the probability of the transport ship to leave the port is first assessed (first activity), then, conditional probability to perform the transfer of piles onto the instllation vessel is performed (second activity).